
The harm argument put forth in this short chapter is mostly included because of its everyday intuitive appeal. I am not aware of any philosopher who adheres to this argument. 

\section{The argument}


\begin{tcolorbox}[enhanced,%fit to height=5cm,
  colback=green!25!black!10!white,colframe=green!75!black,title=Fit box (5cm),
  drop fuzzy shadow,watermark color=white,watermark text=Fit]
\begin{align*}
1)& \text{Causing unnecessary harm is bad} \\
2)& \text{Eating animals causes unnecessary harm } \\
\rightarrow& \text{Therefore, eating animals is bad }
\end{align*}
\end{tcolorbox}


% \begin{tcolorbox}[enhanced,%fit to height=10cm,
%   colback=green!25!black!10!white,colframe=green!75!black,title=Principle of utility (10cm),
%   drop fuzzy shadow,watermark color=white,watermark text=Fit]
%  %\lipsum[1-4]
% “the only purpose for which power can be rightfully exercised over any member of a civi- lised community, against his will, is to prevent harm to others”
% ― John Stuart Mill, On Liberty
% \end{tcolorbox}


% Though Mill is perhaps the most known proponent of the harm principle, to Mill this was not a sufficient principle for morality but merely a heuristic for legal principles. 

Though the argument appears straightforward, it is nevertheless worth clarifying some terminology. The term “bad” is used in a strong sense of "we should not do what is bad". In other words, bad is carries with it a kind of moral force, implying that if somebody accepts that an action has this property they should be compelled not to take that specific action. 

Any one act can have numerous positive and/or negative effects and the argument can still maintain meaning. The simplest way these effects can be aggregated is through additivity, i.e. if one has reason to believe these effects can be added up then one can claim the action is bad in total. 

An example of this is when the act of helping causes harm that is unnecessary for the consequence one aims to achieve with their action. For instance, perhaps I push you out of the way so that you won’t get run over by an incoming car, but as a consequence of my action you lose your hat. It is true that you losing your hat not necessary for being saved from an incoming car. Nevertheless, we can judge a posteriori that it was a necessary consequence of the action taken.

It must be noted that the action itself doesn’t have to always be inadvisable . There may be cases where an action is good and cases where that same action is bad. As such the above argument can be revised to apply only to certain situations. For example, if the action is to "give morphine", it would depend on whether the person in question is in pain or not. 

Harm is an ideal term to use  because of its generality. The argument would also appear to work if the words "pain" or "suffering" were used. However, the use of alternative words might exclude the concept of "killing". Using those words would then make the argument more open to objections by way of empirical methods. For instance, one could just point to some painless way of killing and the argument would instantly fail. The harm formulation can survive such an empirical point. On the other hand, if one attacks a pain formulation that would probably also apply to the harm formulation. 

This generalization also corresponds to what most vegetarians actually hold as their belief. If there was a very ethical farmer that practiced the painless killing of an animal, it is unclear and rather doubtful whether this would have an impact of the perspective held by many vegetarians enough to change their beliefs and proceed with eating that animal.

The problem of "harm" is that it may be general enough to encompass non-conscious agents, such as killing a plant or tree. The argument as presented refers only to animals but may be opposed by asking: "why only animals and not plants?". In this case, the vegetarian may return to the previous standards of "suffering" or "harm". Alternatively, they could commit to "mammalianism", that is, arbitrarily discriminate between organic beings based on whether they are mammals or not. 

However, I suspect the most likely position they will take is that it is not a matter of category but a matter of degree. That is, they will agree that harming plants is bad, but not bad enough considering the benefits of the action. That is, one may think that the value of plants is high, but the value of humans living is higher. I believe this kind of position automatically locks into additivity. 



% The argument can also hold if there are cases where the actions can be positive. There may be a circmustance where the action in question is good and some circmustances where the action is bad(notice that this can only occur in a consequentialist context). In this case our argument can be revised to be only made for the cases where it is bad. Alternatively the argument can again rely on a property of additivitiy to claim that in total the bad that is caused is greater than the good that is caused in the totality of cases. 

\textbf{Harm} is a better term than the alternatives because of its generality. The argument would also seem to work if we used the words "pain" or "suffering". However the use of alternative words might exclude the concept of "killing". Using those words would then make the argument more open to objections via empirical methods. For instance one could just point to some painless way of killing and the argument would instantly fail. The harm formulation can survive such an empirical point. On the other hand if one attacks a pain formulation that would probably also apply to the harm formulation. This generalization also corresponds to what most vegetarians actually believe. If a very ethical farmer showed up that filmed the painless killing of the animal, it is doubtful that many vegetarians would change their mind and eat this specific animal. 

The problem of "harm" is that it may be general enough to encompass non-consious agents, such as killing a plant or tree. The argument as presented makes reference only to animals but somebody might object: "why only animals and not plants?". In this case, the vegetarian may return to the previous standards of "suffering" or "harm". Alternatively they could commit to "mamalianism", that is, arbitrarility discriminate between organic beings based on whether they are mammals or not. However I suspect the most likely position they will take is that it is not a matter of category but a matter of degree. That is, they will agree that harming plants is bad, but not sufficiently bad given the benefits. That is, one may think that the value of plants is high but the value of humans living is higher. I believe this kind of position automatically locks you into additivity.  


% http://www.veganfuturenow.com/answering-the-objections-to-veganism#do-you-want-animals-to-have-the-right-to-get-married-and-vote

% \section{Where does the argument apply? }

% The harm principle as articulated by Mill was the main rherhorical tool used for legalizing homosexuality and is often used to argue for 


\section{Problems}

\subsection{Necesity}

The most obvious problem with the argument is the notion of necessity. A circular definition of the term is: X is necessary if the presence of X is required for a certain other thing to occur. It makes little linguistic sense to talk of necessity without a cause, necessity is a constraint and there must be some objective for the constraint to work on. % Neccesicty definition

For instance, if I want to make a cake it is necessary that I use the ingredients necessary to make the cake. The sentence "flour is necessary to make the flour cake" makes sense. The sentence "flour is necessary" does not make sense in itself. Thereby, it becomes clear that vegetarians are assuming that there is some goal, in this example the cake, which can be achieved through a variety of means. % Taste and neccesicty

What is the "cake" of the harm done to animals? Suppose an agent is trying to get the best "taste" possible, the so called “omega taste”. If the omega taste does not require eating animals, then the argument works. This would be equivalent to saying: "don’t eat animals because there are better tastes out there". If on the other hand the omega taste must include animal flesh, then the argument instantly fails. That is, if I am trying to have the best taste I can, then it IS necessary that I eat animals.% Neccesity and goals

I suspect that the herbivores then have a rather different perspective. They are instead redirecting us to look for another “cake”. A reflexive reaction to this might be "who are they to tell us what our goals should be?". Perhaps they know better than us, either because they have reasoned better or maybe they have information we do not. 

If it is true that they have reasoned better than us, then perhaps this reasoning can also be shared with us, and upon engaging in this reasoning, we can be persuaded to also change our goals \footnote{ Perhaps here we might have a Kantian argument, but Kant famously excluded animals from his categorical imperative. }.. If on the other hand they have better experience than us, then they need only try and help us experience those same things \footnote{It seems to me like vegans are over-represented in urban environments with low animal contact }. 

If it is true that the they have reasoned better than us, then perhaps this reasoning can also be shared with us, and upon bathing in this reasoning, we can be change our goals\ If on the other hand they have better experience than us, then they need only try and help us experience those same things .
%A priori and posteriori

To 
Consequently, it seems to me that this argument fails for the simple reason that it begs the question about what people should pursue.

Perhaps more importantly, neccesity is dynamic not static. For instance it may be that what I want is to live in a community where people look out for each other, it may appear that if I get rid of say bull fighting, we can find other ways to bond, but in practice, when bull fighting was abandoned, the community came apart. Saying something is not neccesary misses the point about what paths one can safely transition to. It may be true that other paths to achieve the same function but they are not avaialble from the current state, or at the very least not avaialable without significant damage. 

So it seems to me that this argument fails for the simple reason that it begs the question about what people should puruse. 

% We should not be trying to get this taste at all but then this would be a different argument entirely. 

% Why do people eat meat? 

% Do people eat meat because of the taste? Though I suspect many people do consiously believe they eat meat because they enjoy the taste, evolutionary reasoning actually works backwards: They like the taste because they meat. In other words, the argument should not be taken at face value, people are comfortable eating meat but the reason they eat meat is not it's taste. For instance when the first humans started eating meat, it is likely they did not have the neccesary genetic make-up to enjoy it's taste, nevertheless those groups that did eat meat survived better and overtime developed the taste buds. 

% So notice what is happening here, a group does something even if it goes against their taste buds, in other words, they put up with it, and overtime this either turns out to have been a good choice or not. This is in contrast to somebody merely satisfying their desires, indeed merely satisfying ones desires implies the lack of change. To repeat, if an organism attempts simply to satisfy it's existing desires and not to stick to things that go against its desires, by definition the organism can only evolve through one avenue, natural selection among desires. 

% This kind of prescription seems to me to be animal like, advocating that humans should refuse non to evolve in a non-desire dimension just seems to be exactly anti-human. Humanity is about cultural evolution, it is about norms that overule our desire. From the evolutionary point of view this allows for quicker adaptation, but from a christian point of view this explains the culture of helping the needy. It refuses to allow for natural selection among desires but insists on cultural selection. 

% This is a more general problem with utilitarianism, it insists that our preferences must be met, it denies the very human stuborness which is the cause of much of our adaptation. 

% This is not to say that taste plays no role. Indeed once we have this evolutionary reasoning clear in our heads we can interpret taste as an attractor, that is, to make experimenting more likely to lead to a meat diet. As such taste can play an important role for habit formation, an invaluable role for new generations.

% Suppose there exists an agent who only changes his behavior if he can find reasons to change behavior. For instance suppose that there are green frogs and red frogs, the red frogs are poison but not the green frogs. This might naturally create an instinct of disgust when seeing red frogs, which might partly carry over to green frogs. Depending on the environment the fine tuning of the disgust instinct may change, for instance if the only thing that can be eaten is green frogs then more evolution will take place to fine tune the instinct to discriminate, but if there are 

% In other words, somebody who reasons about his ethics by definition can't learn about ethics empirically. They can only learn how best to achieve their existing ethics. 

% Imagine that there is a brain that ignores culture and always aims to deduce what it should do. 

% The evolutionary view put the weight on unconcious learning. Indeed an organism that did overrule it's instincts or who reasoned its behavior would not be able to evolve. 

%  that concious learning is less important than unconcious learning. 

%  In other words agent's are not optimizing creatures, they just have a set of habits, there is no sense in speaking of constraints. 

% Is this obvious truth, that people have habits and don't analyze their actions and simply do things, a deathblow to philosophers trying to analyze them? A philosopher may be interested in two distinct things, trying to explain the behavior of the the agents, and trying to convince the agents to change their mind. 

% If the goal of the philosopher is simply to explain the behavior, he is in fact indifferent to how the agent's decide, instead he is interested in studying their behavior and will simply try to re-formulate his theory to say that agents are acting AS IF they maximize their pleasure. This approach is most interesting for those who with a scientific inclination, it can be used to try and predict the behavior. 

% If on the other hand the philosopher is interested in changing the agents mind, then he will try to stop the agent from doing thing unconsiously. This may provoke anger or dismissable from the agent, understandably, a bit like socrates who was known for being really annoying by trying to have people articulate everything. Of course this may be a more dangerous exercise than it seems because making an agent less reliant on one habit may make them doubt their other habits. Of course philosophers may think this is a desirable state of affairs to the desirable, but they are open to Chesterton's fence criticism. 

% But let's play the philosophers game and assume for a moment that people are eating meat because they are maximizing some underlying variable. What is their goal if it is not taste? What else can be the optimand of people? Perhaps people are trying simply to optimize their pleasure, but that would simply result in a similar argument to the "taste" argument. Perhaps they are trying to lead a good life, in which case the vegetarian would have to appeal defining the "good life", something many vegetarians don't wish to do because it makes retaining a subjectivist position difficult. If they are willing to empbrace non-subjectivist positions then they would have to fall to objective standards. Nevertheless the most likely turn of vegetarians after reflecting is to use happiness as the standard. 

% In other words, the vegetarians will simply try to use the utilitarian standard and attempt to convert meat-eaters to adopt this standard. 

% First: https://twitter.com/JoshHochschild/status/1246061518665506816?s=20

% Second: https://twitter.com/diomavro/status/1246497670757302272?s=20


% Third: https://twitter.com/diomavro/status/1246858198688116739?s=20

% https://twitter.com/diomavro/status/1246859165013889024?s=20